TUD Datasets: A collection of benchmark datasets for learning with graphs

### 2020-04-04 main.tex
started text on datasets; added some comments

@@

\begin{abstract}
Recently, there has been an increasing interest in learning with graph data, especially using graph neural networks.  However, the development of meaningful benchmark datasets and standardized evaluation procedures is lagging behind. That is, most paper papers evaluate their methods on small-scale datasets leading to high standard deviations and hard to interpret results, consequently hindering advancements in this area. To address this, we introduce the \textsc{Tud dataset} for graph classification and regression. The dataset consists of over 150 datasets from a wide range of applications and varying sizes. We provide Python-based data loaders, baseline implementations, and evaluation tools. Here, we give an overview of the datasets, evaluation tools, and provide baseline experiments. 
\end{abstract}

@@

Here, we give an overview of \textsc{Tud datasets}. The benchmark collection consists of over 150 datasets from a wide range of domains for supervised learning with graphs, i.e., classificiation and regression. All datasets are provided in a common dataset format at \url{graphlearning.io}, and easily be accessed from popular graph learning frameworks such as \emph{Pytorch Geometric}~\cite{Fey+2019} and \emph{DGL}~\cite{Wan+2019}.

@@

@@

In order to provide meaningful baselines, we provide implementation of common graph kernels was well as GNNs baselines. We have implemented the \new{Weisfeiler-Lehman Subtree}~\cite{Shervashidze2011}, \new{Shortest-path}~\cite{Bor+2005}, \new{Graphket}~\cite{She+2009}, \new{Weisfeiler-Lehman Optimal Assigment}~\cite{Kri+2016} kernel, as well as the higher-order WL kernels~\cite{Mor+2019b}, in \CPP and made them accessable through the Python interface of \textsc{Tud dataset}, see \url{XXX} for further details.  Moreover, all GNN architectures implemented in PyTorch Geometric can be used as baseline as well.

Vertex kernel and edge kernel?

@@

For both methods, we used the evaluation procecude described in~\cref{eval} to optimize hyperparameters and compute accuracies. All experiments can be fulled reprodcued from the scripts provided at \url{XXX}.

>>>>

\newcommand{\nk}[1]{{{\textcolor{brown}{\textbf{[NK:} {#1}\textbf{]}}}}}

@@

\begin{abstract}
Recently, there has been an increasing interest in learning with graph data, especially using graph neural networks.  However, the development of meaningful benchmark datasets and standardized evaluation procedures is lagging behind. That is, most paper papers evaluate their methods on small-scale datasets leading to high standard deviations and hard to interpret results, consequently hindering advancements in this area. To address this, we introduce the \textsc{Tud dataset} for graph classification and regression. The dataset consists of over 150 datasets from a wide range of applications and varying sizes. We provide Python-based data loaders, baseline implementations, and evaluation tools. Here, we give an overview of the datasets, evaluation tools, and provide baseline experiments. 
\nk{Make clear that these are datasets collected from the authors of various papers}
\end{abstract}

@@

Here, we give an overview of \textsc{Tud datasets}. The benchmark collection consists of over 150 datasets from a wide range of domains for supervised learning with graphs, i.e., classificiation and regression. All datasets are provided in a common dataset format at \url{graphlearning.io}, and can easily be accessed from popular graph learning frameworks such as \emph{Pytorch Geometric}~\cite{Fey+2019} and \emph{DGL}~\cite{Wan+2019}.

@@

\subsection{Datasets}

Our collection of datasets covers graphs from various domains, which were provided by different authors. Therefore, they differ regarding the used graph model even within the same domain and the provided annotations, e.g., discrete or continuous node/edge attributes. We give an overview of some representative domains and graph models.

\paragraph{Small molecules.} 
A commonly used class of graph datasets are derived from small molecules with class labels representing, e.g., toxicity or biological activity determined in the context of drug discovery. A molecule is represented by a graph in which vertices take the places of atoms and edges that of chemical bonds. Consequently, the labels indicate atom and bond types, where additional chemical attributes are possible. The graph models differs, e.g., in whether hydrogen atoms represented explicitly by vertices and bonds in aromatic rings are annotated accordingly.
Our collection contains small datasets commonly used in the early graph kernel literature such as \textsc{Mutag}~\citep{Deb+1991} and \textsc{Ptc}~\cite{Helma2001}, medium-sized datasets, e.g., \textsc{Nci1} and \textsc{Nci109}~\citep{Wal+2008,She+2011}, as well as several large datasets derived from the \emph{Tox21 Challenge 2014} or \emph{PubChem}~\citep{Kim2018}. For some classification tasks, the geometrical arrangement of atoms has been determined and should be taken into account in a rotation-invariant manner. In order to achieve this, complete graphs with edges annotated by distances are commonly used~\citep{Kri+2012,Gil+2017}. Our collection contains the four datasets \textsc{BZR}, \textsc{COX2}, \textsc{DHFR}, \textsc{ER} initially published by \citet{Sut+2003} in two versions, with 3d coordinates of atoms and inter-atom distances, respectively, cf.~\citep{Mah+2006,Kri+2012}.

\paragraph{Bioinformatics.}

\paragraph{Computer vision.}
Graph-based methods are widely used in computer vision for various tasks using diverse graph models. Our collection provides several datasets originating from the \emph{IAM Graph Database}~\citep{Riesen2008} such as \textsc{Letter} and \textsc{Fingerprint}. Other datasets represent \textsc{Cuneiform} signs~\citep{Kriege2018}, 3d point clouds for robot grasping tasks (\textsc{FirstMM\_DB}) and semantic image processing (\textsc{MSRC})~\citep{Neu+2016}.

\paragraph{Social networks.}
Several of the provided datasets are derived from social networks
TODO

Recently, temporal graphs were considered, where edges represent the contact or interaction between two individuals at a certain point in time. Such graphs are of interest when studying dissemination processes such as epidemics, information and fake news. We provide temporal graph classification datasets derived from \textsc{Tumblr}, \textsc{Dblp} and \textsc{Facebook} as well as contacts in a \textsc{Highschool} and at the \textsc{Infectious} exhibition~\citep{Oettershagen2019}.

@@

In order to provide meaningful baselines, we provide implementation of common graph kernels was well as GNNs baselines. We have implemented the \new{Weisfeiler-Lehman Subtree}~\cite{Shervashidze2011}, \new{Shortest-path}~\cite{Bor+2005}, \new{Graphlet}~\cite{She+2009} \nk{Das ist eine Variante mit Labeln und 3 Knoten oder?}, \new{Weisfeiler-Lehman Optimal Assigment}~\cite{Kri+2016} kernel, as well as the higher-order WL kernels~\cite{Mor+2019b}, in \CPP and made them accessable through the Python interface of \textsc{Tud dataset}, see \url{XXX} for further details.  Moreover, all GNN architectures implemented in PyTorch Geometric can be used as baseline as well.

Vertex kernel and edge kernel? \nk{Wäre interessant!}

@@

For both methods, we used the evaluation procecude described in~\cref{eval} to optimize hyperparameters and compute accuracies. All experiments can be reproduced using the scripts provided at \url{XXX}.
